The Results of SAT Competition 2020

### 2020-07-31 slides/satcomp20slides.tex
cloud scores

\begin{frame}{Parallel Track SAT -- Results}
The Top 3 solvers of the Parallel Track SAT are:
\begin{itemize}
\item[1]<4-> {\bf P-MCOMSPS-STR-32} (PAR-2: 2853, 153 solved)\\
by Vincent Vallade, Ludovic Le Frioux, Souheib Baarir,\\Julien Sopena, and Fabrice Kordon
\item[2]<3-> {\bf PaInleSS\_ExMapleLCMDistChronoBT} (PAR-2: 2913, 154 solved)\\
by Rodrigue Konan Tchinda and Cl\'ementin Tayou Djamegni
\item[3]<2-> {\bf abcd-para-scavel} (PAR-2: 3405, 143 solved)\\
by Zhihui Li, Guanfeng Wu, Yanh Xu, and Qingshan Chen
\end{itemize}
\end{frame}

@@

\begin{frame}{Parallel Track ALL -- Results}
The Top 3 solvers of the Parallel Track ALL are:
\begin{itemize}
\item[1]<4-> {\bf P-MCOMSPS-STR-32} (PAR-2: 3291, 284 solved)\\
{\bf P-MCOMSPS-STR-64} (PAR-2: 3689, 272 solved)\\
by Vincent Vallade, Ludovic Le Frioux, Souheib Baarir,\\Julien Sopena, and Fabrice Kordon
\item[2]<3-> {\bf Plingeling} (PAR-2: 3718, 270 solved)\\
by Armin Biere
\item[3]<2-> {\bf abcd-para-scavel} (PAR-2: 3797, 270 solved)\\
by Zhihui Li, Guanfeng Wu, Yanh Xu, and Qingshan Chen
\end{itemize}
\end{frame}

@@

\item[1]<4-> {\bf mallob-mono} (PAR-2: 2429, 306 solved)\\
by Dominik Schreiber
\item[2]<3-> {\bf TopoSAT2} (PAR-2: 3024, 283 solved)\\
by Thorsten Ehlers, Mitja Kulczynski, Dirk Nowotka, and Philipp Sieweck
\item[3]<2-> {\bf Slime} (PAR-2 4208, 239 solved)\\
by Oscar Riveros
\end{itemize}

>>>>

\begin{frame}{Parallel Track SAT -- Results}
The Top 3 solvers of the Parallel Track SAT are:
\begin{itemize}
\item[1]<4-> {\bf P-MCOMSPS-STR-32} (PAR-2: 2853, 153 solved)\\
by Vincent Vallade, Ludovic Le Frioux, Souheib Baarir,\\Julien Sopena, and Fabrice Kordon
\item[2]<3-> {\bf PaInleSS\_ExMapleLCMDistChronoBT} (PAR-2: 2913, 154 solved)\\
by Rodrigue Konan Tchinda and Cl\'ementin Tayou Djamegni
\item[3]<2-> {\bf Plingeling} (PAR-2: 3805, 133 solved)\\
by Armin Biere
%\item[3]<2-> {\bf abcd-para-scavel} (PAR-2: 3405, 143 solved)\\
%by Zhihui Li, Guanfeng Wu, Yanh Xu, and Qingshan Chen
\end{itemize}
\end{frame}

@@

\begin{frame}{Parallel Track ALL -- Results}
The Top 3 solvers of the Parallel Track ALL are:
\begin{itemize}
\item[1]<4-> {\bf P-MCOMSPS-STR-32} (PAR-2: 3291, 284 solved)\\
{\bf P-MCOMSPS-STR-64} (PAR-2: 3689, 272 solved)\\
by Vincent Vallade, Ludovic Le Frioux, Souheib Baarir,\\Julien Sopena, and Fabrice Kordon
\item[2]<3-> {\bf Plingeling} (PAR-2: 3718, 270 solved)\\
by Armin Biere
\item[3]<2-> {\bf ManyGlucose-32} (PAR-2: 3985, 260 solved)\\
by Hidetomo Nabeshima and Katsumi Inoue
%\item[3]<2-> {\bf abcd-para-scavel} (PAR-2: 3797, 270 solved)\\
%by Zhihui Li, Guanfeng Wu, Yanh Xu, and Qingshan Chen
\end{itemize}
\end{frame}

@@

\item[1]<4-> {\bf mallob-mono} (PAR-2: 583, 299 solved)\\
by Dominik Schreiber
\item[2]<3-> {\bf TopoSAT2} (PAR-2: 706, 278 solved)\\
by Thorsten Ehlers, Mitja Kulczynski, Dirk Nowotka, and Philipp Sieweck
\item[3]<2-> {\bf Slime} (PAR-2 1057, 214 solved)\\
by Oscar Riveros
\end{itemize}
